% !TEX program = xelatex

\documentclass{resume}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Alexandru Dorel Ungureanu}

\basicInfo{
  \email{u95.alexandru@gmail.com} \textperiodcentered\ 
  \phone{(+39) 351-788-5640} \textperiodcentered\ 
  \linkedin[Alexandru Ungureanu]{https://www.linkedin.com/in/alexandru-ungureanu-6b83a6235/}}

\section{\faUser\ Summary}
Motivated and detail-oriented full-stack web developer with 3+ years of experience in creating dynamic and efficient web solutions. Passionate about learning and implementing new technologies to solve real-world problems. Excels in both collaborative team environments and independent projects.

\vspace{1em}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Sainsbury's} Hoddesdon, United Kingdom}{Jan. 2018 -- 2021}
\role{Warehouse Operator}{Crane Operator}  
Operated heavy equipment to manage warehouse logistics efficiently.

\vspace{1em}

\datedsubsection{\textbf{Freelance Web Developer} Buzau, Romania}{2021 -- 2022}
\begin{itemize}
  \item Built and deployed responsive landing pages using HTML, CSS, and JavaScript for local businesses.
  \item Managed and updated client websites, improving performance and SEO rankings.
  \item Gained experience in collaborating with clients to translate their needs into functional solutions.
\end{itemize}

\vspace{1em}

\datedsubsection{\textbf{Oltrematica S.R.L} Pescara, Italy}{2022 -- Present}
\role{Full Stack Web Developer}{}  
\begin{itemize}
\item Built responsive front-end interfaces using Vue 3 and Tailwind CSS.
  \item Developed scalable back-end services with Laravel and Node.js, improving system efficiency by 30%.
  \item Integrated REST APIs, managed databases, and deployed applications on Linux servers.
  \item Set up production servers and configured CI/CD pipelines to automate builds, testing, and deployments, reducing deployment times by 40%.
\end{itemize}

\vspace{1em}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming: PHP, JavaScript, TypeScript, Java, Go, Kotlin, SQL.
  \item Frameworks \& Libraries: Laravel, Vue 3, Node.js, Spring Boot, Express.js.
  \item DevOps \& Deployment: Docker, Nginx, GitHub Actions, Linux Administration.
  \item Databases \& APIs: MySQL, REST APIs, Google APIs.
  \item Other Tools: Git, Photoshop, i18n.
  \item Operating Systems: Linux (expert), Windows, macOS.
\end{itemize}

\vspace{1em}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Website: \url{https://alexplayground.dev/}
  \item GitHub: \url{https://github.com/u-alexandru}
  \item Languages: English (Fluent), Italian (Fluent), Romanian (Native), Japanese (N5)
\end{itemize}

\end{document}
